\section*{Preface}
\thispagestyle{empty}
\setcounter{page}{0}

This project is the result of weeks of collaborative work between the authors. Designing, discussing and testing the different modules that conform it has helped us to better understand the course as well as to develop crucial key skills such as communication, teamwork, problem solving and time management. \medskip 

Before diving into the document there are some remarks that must be made to better understand the assignment:

\begin{itemize}
    \item Most of the GALs that we have used in this project use Finite State Machines to perform their different duties. In almost of all them, a synchronous reset is used in lieu of an asynchronous one. The decision was intentional since most of the FSMs end in a final steady state that waits for the reset signal to restart themselves. Besides, the clock frequency is very fast for a GAL, so it is almost impossible for them to miss the reset signal. We have tested this extensively and found no problem whatsoever in the execution of the code.
    
    \item All of the images, tables, and figures are vectorial, so feel free to zoom in if something is not big enough.
    
    \item There are hyperlinks in most of the pages that will take you to the specific section in which the mentioned topic is explained in more detail. We recommend that you use a PDF Viewer such as Adobe Acrobat or similar.
    
    \item We have also added hyperlinks to the references that we have used to elaborate the assignment. The full references list can be found at the end of the document.
    
    \item The project files can be found \textbf{\href{https://drive.google.com/drive/folders/1CNiwcC9CncEdfxiFuib3KTSMWgVY08vC?usp=sharing}{here}}. We strongly suggest having the Proteus file open alongside the PDF.
    
    \item In the Proteus file you will find instructions on how to operate the system.
\end{itemize}

\medskip

We sincerely hope you like the project. Please, feel free to comment on how you would improve certain aspects if you find it necessary. We are aware of the extension of the document and would like to apologize beforehand.\bigskip 

Finally, let us end this project and also this subject by saying that it has truly been a great pleasure having you as a teacher. We hope that somehow our paths cross again in the future. 


\clearpage